A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-18 main.Rmd
section 3.1 done

Time provides a contextual basis for temporal data. A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than a masked attribute, which makes time visible and accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indexes. The accessibility of tsibble index motivates data analysis towards transparency and human readability. When the "index" used to be employed as meta information, it created an obstacle for analysts to write these simple queries in a programmatic manner, which should be discouraged from an analytic point of view.

A variable number of time representation is spotted in the wild. Date-time, universally accepted across systems, is the most commonly used type for representing time. Date-time also typically associates with a time zone with adjustments like summer time. This diversity and time zone is respected and taken into consideration for the *tsibble*'s index.

>>>>

Time provides a contextual basis for temporal data. A variable representing time is essential for a tsibble, and is referred to as an "index". The "index" is an intact data column rather than a masked attribute, which makes time visible and accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indexes. The accessibility of tsibble index motivates data analysis towards transparency and human readability. When the "index" used to be employed as meta information, it created an obstacle for analysts to write these simple queries in a programmatic manner, which should be discouraged from an analytic point of view.

A variable number of time representations is spotted in the wild. A Date-time object, universally accepted across computing systems, is the most commonly used type for representing time. Date-time also typically associates with a time zone with adjustments like summer time. This diversity and time zone is acknowledged and considered the building block for  *tsibble*'s index.
